Empirical normative theories

### 2020-07-02 simple.tex
Trying def attack-exists using coalitions (but complex)

\subsection{Falsifiability}
Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$, and say that $\ar_1$ is an effective attack against $\ar_0$ (from $i$’s perspective).

@@

Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$. Abusing notation, given $\args_1 \subseteq \allargs$, I write $\args_1 \cap \hist$ to designate $\args_1 \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.

>>>>

\subsection{Falsifiability}
Given $\hist \in \allhist$, $\hist(\intvl{1, l(\hist)})$, where $l(\hist) \in \N$ is the length of the sequence $\hist$, denotes the range of $\hist$, that is, all arguments contained in the sequence $\hist$. Abusing notation, given $\args \subseteq \allargs$, I write $\args \cap \hist$ to designate $\args \cap \hist(\intvl{1, l(\hist)})$, therefore using simply $\hist$ in that expression to denote the \emph{range} of $\hist$.

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs, \args \subseteq \allargs$, with $\args$ finite, define recursively, on the basis of the cardinality of $\args$: $\emptyset \nibeatsi \ar_0$, and $\args \ibeatsi \ar_0$ iff $[\args \subseteq {\gbeatsinv}(\ar_0)] \land [\exists \hist \in \allhist \suchthat (\hist \cap {\gbeatsinv}(\ar_0) \subseteq \args \land \ar_0 \in \histend)] \land [\forall \args' \subset \args: \args' \nibeatsi \ar_0]$.

TODO claim that if $\hist \nileadstoi \phi$, with $\ar_1, \ar'_1 \in \hist$ and $\ar_0 \in \histend$, then $\ar_2$ is among the defensors, or $\ar'_2$ is.

@@
